|

### 2019-07-15 inst/manuscript/manuscript.Rmd
Update imputation method in supplement

```{r table1}
tab1_cap <- "\\textbf{Candidate positive protein markers for 
             \\textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \\textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (ref:footnote1) or in the 
             \\textit{C. albicans} UniProt reference proteome (UP000000559) 
             (ref:footnote2). The log\\textsubscript{2} ratio of the abundance 
             (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
             whole cell lysate (WCL) for each strain is listed. \`\`ex\" 
             indicates where a protein was only quantified in the EV fraction 
             and not the WCL for that strain. The \`\`TM\" column indicates the 
             number of transmembrane domains for each protein as annotated in 
             UniProt. \`\`SP\" indicates whether a protein is annotated as 
             having a signal peptide according to UniProt. \`\`VDM\" shows 
             whether a protein has previously been detected in vesicle-depleted 
             culture media (i.e. the proteins may also be in the soluble secretome) 
             (ref:table1). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in supplemental Figure S1."

# draw table 1
knitr::kable(marker_longlist2[ ,-9],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1,2, 6,7, 13,14,15, 18,19,20,21,22,23, 27, 32, 
                   38,39,40, 42,43,44,45), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 23) %>% 
  pack_rows("Cell wall, cell surface", 24, 36) %>% 
  pack_rows("Endoplasmic reticulum", 37, 41) %>% 
  pack_rows("Endosome, Golgi, transport vesicle", 42, 44) %>% 
  pack_rows("Vacuole", 45, 45) %>% 
  pack_rows("Mitochondrion", 46, 47) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} ortholog as 
                         annotated in the Candida Genome Database 
                        (ref:footnote1).", 
                        "Protein localisation was obtained from the GO Cellular
                        Component annotation in UniProt (ref:footnote2).", 
                        "Presence of transmembrane domains and absence of a 
                        signal peptide was predicted using TOPCONS2 
                        (ref:footnote3).",
                        "The name Evp1 for the protein encoded by orf19.6741 
                        was proposed in the present study."), 
           escape = FALSE, 
           threeparttable = TRUE)
```

>>>>

```{r table1}
tab1_cap <- "\\textbf{Candidate positive protein markers for 
             \\textit{C. albicans} EVs.} This list of proteins consists of 
             those that were found to be exclusive to EVs or significantly 
             enriched in EVs across the four \\textit{C. albicans} strains 
             examined in this study. Proteins are grouped according to their 
             subcellular localisation as annotated in the Candida Genome 
             Database (candidagenome.org) (ref:footnote1) unless otherwise 
             indicated. The log\\textsubscript{2} ratio of the abundance 
             (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
             whole cell lysate (WCL) for each strain is listed. \`\`ex\" 
             indicates where a protein was only quantified in the EV fraction 
             and not the WCL for that strain. The \`\`TM\" column indicates the 
             number of transmembrane domains for each protein as annotated in 
             UniProt. \`\`SP\" indicates whether a protein is annotated as 
             having a signal peptide according to UniProt. \`\`VDM\" shows 
             whether a protein has previously been detected in vesicle-depleted 
             culture media (i.e. the proteins may also be in the soluble secretome) 
             (ref:table1). Underlined proteins are those identified as the 
             best candidates for positive EV markers according to the 
             criteria depicted in supplemental Figure S1."

# draw table 1
knitr::kable(marker_longlist2[ ,-9],
             caption = tab1_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE)  %>% 
  row_spec(row = c(1,2, 6,7, 13:15, 18:23, 27, 32, 38:40, 42:45), 
           underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 2), escape = FALSE) %>% 
  kable_styling(font_size = 8) %>% 
  pack_rows("Plasma membrane", 1, 23) %>% 
  pack_rows("Cell wall, cell surface", 24, 36) %>% 
  pack_rows("Endoplasmic reticulum", 37, 41) %>% 
  pack_rows("Endosome, Golgi, transport vesicle", 42, 44) %>% 
  pack_rows("Vacuole", 45, 45) %>% 
  pack_rows("Mitochondrion", 46, 47) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} homolog as 
                         annotated in the Candida Genome Database 
                        (ref:footnote1).", 
                        "Protein localisation was obtained from the GO Cellular
                        Component annotation in the \\\\textit{C. albicans} 
                        UniProt reference proteome UP000000559 (ref:footnote2).", 
                        "Presence of transmembrane domains and absence of a 
                        signal peptide was predicted using TOPCONS2 
                        (ref:footnote3).",
                        "The name Evp1 for the protein encoded by orf19.6741 
                        was proposed in the present study."), 
           escape = FALSE, 
           threeparttable = TRUE)
```

### 2019-07-15 inst/manuscript/manuscript_supplement.Rmd
Update imputation method in supplement

---
title: | 
   **Supplement to: Protein markers for *Candida albicans* EVs include
   claudin-like Sur7 family proteins and Rho GTPases**
author: | 
   | Charlotte Dawson^a^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
     Pierre Faou^b^,
   | Marilyn Anderson^a^, Mark Bleackley^a^
date: | 
   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
     Molecular Science, La Trobe University, 
     Melbourne, 3086, Victoria, Australia*
   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
     Molecular Science, La Trobe University, Melbourne, 
     3086, Victoria, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{Defining \textit{Candida albicans} EV protein markers}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \newcommand{\beginsupplement}{
      \setcounter{table}{0} 
      \renewcommand{\thetable}{S\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{S\arabic{figure}}
    }
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

@@

# set seed for random number generation
set.seed(1)

# reference external R script with protein function lists
knitr::read_chunk('components/protein_funs.R')
```

@@

# see limma user guide section 9.2 for more info about DE
# create design matrix
b_samp <- data.frame(T = (rep(c("EV", "WCL"), each = 5)))

@@

# construct table S2
wcl_longlist <- wcl_candidates %>% 
  mutate(Function = match_id(Name, uniprot, "CGD_gene_name", 
                             "Protein_name", concat = TRUE, str_split = FALSE),
         DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", 
                          "logFC", concat = TRUE, str_split = FALSE), 
         A9 = match_id(Name, a9_res, "CGD_gene_name", 
                       "logFC", concat = TRUE, str_split = FALSE), 
         A1 = match_id(Name, a1_res, "CGD_gene_name", 
                       "logFC", concat = TRUE, str_split = FALSE), 
         DAY.B = match_id(Name, biofilm_res, "CGD_gene_name", 
                          "logFC", concat = TRUE, str_split = FALSE), 
         TM = match_id(Name, uniprot, "CGD_gene_name", "Transmembrane"), 
         SP = match_id(Name, uniprot, "CGD_gene_name", "Signal_peptide")) %>% 
  mutate_at(.vars = vars(DAY.Y, DAY.B, A1, A9), 
            .funs = list(~ sprintf(as.numeric(.), fmt = "%#.2f"))) %>% 
  mutate_at(.vars = vars(DAY.Y, DAY.B, A1, A9), 
            .funs = list(~ case_when(. == "NA" ~ "ex", 
                                     TRUE ~ as.character(.)))) %>% 
  mutate(TM = stringr::str_count(TM, "Helical"), 
         SP = case_when(grepl("SIGNAL", SP) ~ "Y", 
                        TRUE ~ ""), 
         TM = case_when(TM == 0 ~ "", 
                        TRUE ~ as.character(TM))) %>% 
  rename("DAY Y" = DAY.Y, "DAY B" = DAY.B) %>% 
  arrange(Name)

# load vector of protein functions from external R script
<<fun_list2>>

# add proper protein functions to table 1
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
wcl_longlist2 <- wcl_longlist %>% 
  mutate(Function = function_desc2, 
         VDM = c(rep("", 40)), 
         pack_row = c(rep(4, 2), 3, rep(2, 2), 7, rep(1, 2), rep(7, 2), 1, 
                      rep(2, 4), 7, 3, 2, 5, 1, 
                      2, 6, 2, 1, 7, rep(1, 2), 2, 1, 5, 1, 
                      1, 6, 2, 1, rep(8, 2), rep(1, 3))) %>% 
  arrange(pack_row)
```

@@

(ref:footnote2) [@almagroarmenteros2017]

(ref:footnote3) [@savojardo2018]

```{r tableS2}
tabs2_cap <- "\\textbf{Candidate negative protein markers for 
              \\textit{C. albicans} EVs.} This list of proteins consists of 
              those that were found to be exclusive to whole cell lysate (WCL) 
              or significantly enriched in WCL across the four 
              \\textit{C. albicans} strains examined in this study. Proteins 
              are grouped according to their subcellular localisation as 
              annotated in the Candida Genome Database (candidagenome.org) 
              (ref:footnote1). The log\\textsubscript{2} ratio of the abundance 
              (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
              WCL for each strain is listed. A negative value indicates that a 
              protein was enriched in WCL compared to EV. \`\`ex\" indicates 
              where a protein was only quantified in the WCL fraction and not 
              in EVs for that strain. The \`\`TM\" column indicates the number 
              of transmembrane domains for each protein as annotated in 
              UniProtKB. \`\`SP\" indicates whether a protein is annotated as 
              having a signal peptide according to UniProtKB. \`\`VDM\" shows 
              whether a protein has previously been detected in 
              vesicle-depleted culture media (i.e. the proteins may also be in 
              the soluble secretome) (ref:table1). Underlined proteins are 
              those identified as the best candidates for negative
              EV markers according to the criteria depicted in Figure S1."

# draw table S2
knitr::kable(wcl_longlist2[, -10], 
             caption = tabs2_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE) %>% 
  row_spec(row = c(20, 25, 29, 36), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 3), escape = FALSE) %>% 
  kable_styling(font_size = 8, 
                latex_options = c("HOLD_position")) %>% 
  pack_rows("Cytoplasm", 1, 14) %>% 
  pack_rows("Mitochondria", 15, 25) %>% 
  pack_rows("Nucleus", 26, 27) %>% 
  pack_rows("Vacuole", 28, 29) %>% 
  pack_rows("Peroxisome", 30, 31) %>% 
  pack_rows("Proteasome", 32, 33) %>% 
  pack_rows("Cell wall, cell surface, fungal biofilm matrix", 34, 38) %>% 
  pack_rows("Ribosome", 39, 40) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} ortholog as 
                         annotated in the Candida Genome Database 
                         (ref:footnote1)", 
                        "Protein localisation was predicted using DeepLoc-1.0 
                         (ref:footnote2)", 
                        "Protein localisation was predicted using BUSCA 
                         (ref:footnote3)"), 
           escape = FALSE, 
           threeparttable = TRUE)
```

>>>>

---
title: | 
   **Supplement to: Protein markers for *Candida albicans* EVs include
   claudin-like Sur7 family proteins and GTPases**
author: | 
   | Charlotte Dawson^a^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
     Pierre Faou^b^,
   | Marilyn Anderson^a^, Mark Bleackley^a^
date: | 
   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
     Molecular Science, La Trobe University, 
     Melbourne, 3086, Victoria, Australia*
   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
     Molecular Science, La Trobe University, Melbourne, 
     3086, Victoria, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/molecular-and-cellular-proteomics.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[L]{Defining \textit{Candida albicans} EV protein markers}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \newcommand{\beginsupplement}{
      \setcounter{table}{0} 
      \renewcommand{\thetable}{S\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{S\arabic{figure}}
    }
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

@@

# set seed for random number generation
set.seed(1)
```

@@

# see limma user guide section 9.2 for more info about DE
# create design matrix
b_samp <- data.frame(T = rep(c("EV", "WCL"), each = 5))

@@

# construct table S2
wcl_longlist <- wcl_candidates %>% 
  mutate(DAY.Y = match_id(Name, yeast_res, "CGD_gene_name", 
                          "logFC", concat = TRUE, str_split = FALSE), 
         A9 = match_id(Name, a9_res, "CGD_gene_name", 
                       "logFC", concat = TRUE, str_split = FALSE), 
         A1 = match_id(Name, a1_res, "CGD_gene_name", 
                       "logFC", concat = TRUE, str_split = FALSE), 
         DAY.B = match_id(Name, biofilm_res, "CGD_gene_name", 
                          "logFC", concat = TRUE, str_split = FALSE), 
         TM = match_id(Name, uniprot, "CGD_gene_name", "Transmembrane"), 
         SP = match_id(Name, uniprot, "CGD_gene_name", "Signal_peptide")) %>% 
  mutate_at(.vars = vars(DAY.Y, DAY.B, A1, A9), 
            .funs = list(~ sprintf(as.numeric(.), fmt = "%#.2f"))) %>% 
  mutate_at(.vars = vars(DAY.Y, DAY.B, A1, A9), 
            .funs = list(~ case_when(. == "NA" ~ "ex", 
                                     TRUE ~ as.character(.)))) %>% 
  mutate(TM = stringr::str_count(TM, "Helical"), 
         SP = case_when(grepl("SIGNAL", SP) ~ "Y", 
                        TRUE ~ ""), 
         TM = case_when(TM == 0 ~ "", 
                        TRUE ~ as.character(TM))) %>% 
  rename("DAY Y" = DAY.Y, "DAY B" = DAY.B) %>% 
  arrange(Name)

# load .csv file with table S2 labels
wcl_labels <- read.csv("components/tableS2.csv", stringsAsFactors = FALSE) %>% 
  mutate(Function = case_when(Superscript == "a" ~ paste0(Function, 
                                                          footnote_marker_alphabet(1)), 
                              Superscript == "b" ~ paste0(Function, 
                                                          footnote_marker_alphabet(2)),
                              Superscript == "c" ~ paste0(Function, 
                                                          footnote_marker_alphabet(3)), 
                              TRUE ~ as.character(Function)), 
         VDM = c(rep("", 62)))

# add proper protein functions to table S2
# also add vesicle depleted supernatant info and 
# group proteins according to localisation
wcl_longlist2 <- match_id_multi(df = wcl_longlist, 
                                id = "Name", 
                                ref = wcl_labels, 
                                match = "Name", 
                                new = c("Function", "Loc_num", "VDM"), 
                                str_split = FALSE) %>% 
  select(Name, Function, everything()) %>% 
  arrange(Loc_num)
```

@@

(ref:footnote2) [@theuniprotconsortium2019]

```{r tableS2}
tabs2_cap <- "\\textbf{Candidate negative protein markers for 
              \\textit{C. albicans} EVs.} This list of proteins consists of 
              those that were found to be exclusive to whole cell lysate (WCL) 
              or significantly enriched in WCL across the four 
              \\textit{C. albicans} strains examined in this study. Proteins 
              are grouped according to their 
              subcellular localisation as annotated in the Candida Genome 
              Database (candidagenome.org) (ref:footnote1) unless otherwise 
              indicated. The log\\textsubscript{2} ratio of the abundance 
              (mean MaxQuant LFQ intensity) of each protein in EVs compared to 
              WCL for each strain is listed. A negative value indicates that a 
              protein was enriched in WCL compared to EV. \`\`ex\" indicates 
              where a protein was only quantified in the WCL fraction and not 
              in EVs for that strain. The \`\`TM\" column indicates the number 
              of transmembrane domains for each protein as annotated in 
              UniProtKB. \`\`SP\" indicates whether a protein is annotated as 
              having a signal peptide according to UniProtKB. \`\`VDM\" shows 
              whether a protein has previously been detected in 
              vesicle-depleted culture media (i.e. the proteins may also be in 
              the soluble secretome) (ref:table1). Underlined proteins are 
              those identified as the best candidates for negative
              EV markers according to the criteria depicted in Figure S1."

# draw table S2
knitr::kable(wcl_longlist2[, -9], 
             caption = tabs2_cap, 
             format = "latex", 
             booktabs = TRUE, 
             longtable = TRUE, 
             linesep = "", 
             escape = FALSE) %>% 
  row_spec(row = c(26, 32, 36:38, 42, 58), underline = TRUE) %>% 
  add_header_above(c(" " = 2, 
                     "log\\\\textsubscript{2}(fold change) EV vs WCL" = 4, 
                     " " = 3), escape = FALSE) %>% 
  kable_styling(font_size = 8, 
                latex_options = c("HOLD_position")) %>% 
  pack_rows("Cytoplasm", 1, 13) %>% 
  pack_rows("Cytosol and mitochondria", 14, 16) %>% 
  pack_rows("Mitochondria", 17, 32) %>% 
  pack_rows("Nucleus", 33, 34) %>% 
  pack_rows("Vacuole", 35, 38) %>% 
  pack_rows("Cell wall, cell surface, fungal biofilm matrix", 39, 50) %>% 
  pack_rows("Proteasome", 51, 54) %>% 
  pack_rows("Cytoplasmic stress granule", 55, 56) %>% 
  pack_rows("Peroxisome", 57, 57) %>% 
  pack_rows("Actin cortical patch", 58, 58) %>% 
  pack_rows("Unknown", 59, 62) %>% 
  footnote(alphabet = c("Protein localisation was inferred from sequence 
                         similarity with \\\\textit{S. cerevisiae} homolog as 
                         annotated in the Candida Genome Database 
                         (ref:footnote1)", 
                        "Protein localisation was obtained from the GO Cellular
                        Component annotation in the \\\\textit{C. albicans} 
                        UniProt reference proteome UP000000559 (ref:footnote2).", 
                        "Protein and has no Cellular Component annotation in 
                         the Candida Genome Database or UniProt reference 
                        proteome."), 
           escape = FALSE, 
           threeparttable = TRUE)
```
